### 2017-11-07 submission/manuscript.Rmd
complete supplemental fig legend

**Figure S4: **

**Figure S5: **

**Figure S6: **

**Figure S7: **

**Figure S8: **

>>>>

**Figure S4: Random Forest Prediction Success Using Genera for each Stool Study.** A) AUC for prediction in Adenoma using all genera or CRC associated genera only. B) AUC for prediction in Carcinoma using all genera or CRC associated genera only. The dotted line represents an AUC of 0.5. The x-axis is the data set in which the model was initially trained on.

**Figure S5: Random Forest Prediction Success of Carcinoma Using Genera for each Tissue Study.** A) AUC for prediction in unmatched tissue for all genera or CRC associated genera only. B) AUC for prediction in matched tissue using all genera or CRC associated genera only. The dotted line represents an AUC of 0.5. The x-axis is the data set in which the model was initially trained on.

**Figure S6: Random Forest Prediction Success of Adenoma Using Genera for each Tissue Study.**

### 2017-11-07 submission/manuscript.tex
complete supplemental fig legend

\textbf{Figure S4: }

\textbf{Figure S5: }

\textbf{Figure S6: }

\textbf{Figure S7: }

\textbf{Figure S8: }

>>>>

\textbf{Figure S4: Random Forest Prediction Success Using Genera for
each Stool Study.} A) AUC for prediction in Adenoma using all genera or
CRC associated genera only. B) AUC for prediction in Carcinoma using all
genera or CRC associated genera only. The dotted line represents an AUC
of 0.5. The x-axis is the data set in which the model was initially
trained on.

\textbf{Figure S5: Random Forest Prediction Success of Carcinoma Using
Genera for each Tissue Study.} A) AUC for prediction in unmatched tissue
for all genera or CRC associated genera only. B) AUC for prediction in
matched tissue using all genera or CRC associated genera only. The
dotted line represents an AUC of 0.5. The x-axis is the data set in
which the model was initially trained on.

\textbf{Figure S6: Random Forest Prediction Success of Adenoma Using
Genera for each Tissue Study.}
